Faithful Model Explanations through\\ Energy-Constrained Conformal Counterfactuals\footnote{This is a pre-print.}

### 2023-12-17 paper/partials/appendix.tex
more minor updates

Contrary to existing work, we have not typically used the entire minibatch of training data for the generative loss component but found that using a subset of the minibatch was often sufficient in attaining decent generative performance (Table~\ref{tab:ebmparams}). This has helped to reduce the computational burden for our models, which should make it easier for others to reproduce our findings. Figures~\ref{fig:mnist-gen} and~\ref{fig:moons-gen} show generated samples for our \textit{MNIST} and \textit{Moons} data, to provide a sense of their generative property.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{../www/moons_generated_JEM.png}
  \caption{Conditionally generated samples (stars) for our \textit{Moons} data using a JEM.}\label{fig:moons-gen}
\end{figure}
\subsubsection{Inference: Quantifying Models' Generative Property}

>>>>

Contrary to existing work, we have not typically used the entire minibatch of training data for the generative loss component but found that using a subset of the minibatch was often sufficient in attaining decent generative performance (Table~\ref{tab:ebmparams}). This has helped to reduce the computational burden for our models, which should make it easier for others to reproduce our findings. Figures~\ref{fig:mnist-gen} and~\ref{fig:poc-gen} show generated samples for our \textit{MNIST} and \textit{Moons} data, to provide a sense of their generative property.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{../www/poc_conditional_samples.png}
  \caption{Conditionally generated samples (stars) for our \textit{Linearly Separable} data using a JEM.}\label{fig:poc-gen}
\end{figure}
\subsubsection{Inference: Quantifying Models' Generative Property}
